---
title: "Data 607 Hw 2"
author: "Al Haque"
date: "2/9/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Intro:
  I read a csv file from R and I wanted to learn some basic information on the data I collected from my friends. I was curious on the average rating of each movie my friends watched and what movies my friends didn't watched. After doing some data cleaning I then graphed the results on a bar graph. 



### Reading a csv file to R  

  I exported my sql data into a csv file and I placed the csv file on Github. I then made R read the csv file on Github and then I placed all that data into a data frame called Mysql. 

```{r cars}
library(tidyverse)
mysql <- read.csv("https://raw.githubusercontent.com/AldataSci/Assignment2-607-/main/Homework2%5B607%5D.csv",header=TRUE,sep=",")
```


### Average Rating of Movies My Friends Watched
  I removed all the null values from my data and I was curious to see what the average rating of each movie was between my friends 

```{r}
avg_mov <- mysql %>%
  group_by(movie) %>%
  filter(Stars != "NULL") %>%
  summarise(avg= mean(as.integer(Stars)))
avg_mov

```

  Here I graphed my data and not surprisingly Spider-Man was watched by all my friends and they also rated it very highly with a rating of 4.8

```{r}
library(ggplot2)
ggplot(data=avg_mov, aes(x=movie,y=avg , fill=movie)) + 
  coord_flip() +
  geom_bar(stat="identity")
```

### Movies my Friends did not watched and how many didn't watch
  I was curious to see which movies my friends did not watch so I aggregated the data by movie, I filtered the condition where the stars were null and I counted how many people did not see which movies. 4 of my friends did not watch No Time to Die and one of my friend did not watch dune.


```{r}
nul <- mysql %>%
  group_by(movie) %>%
  filter(Stars=="NULL") %>%
  count(Stars,sort=TRUE)
nul
```

  Here I graphed my results in another bar graph. 

```{r}
library(ggplot2)
ggplot(data=nul,aes(x=movie,y=n,fill=movie)) +
  geom_bar(stat="Identity")
```

